+++
# A Demo section created with the Blank widget.
# Any elements can be added in the body: https://sourcethemes.com/academic/docs/writing-markdown-latex/
# Add more sections by duplicating this file and customizing to your requirements.

widget = "blank"  # See https://sourcethemes.com/academic/docs/page-builder/
headless = false  # This file represents a page section.
active = true  # Activate this widget? true/false
weight = 30  # Order that this section will appear.

title = "Detailed program"
subtitle = ""

[design]
  # Choose how many columns the section has. Valid values: 1 or 2.
  columns = "1"

[design.background]
  # Apply a background color, gradient, or image.
  #   Uncomment (by removing `#`) an option to apply it.
  #   Choose a light or dark text color by setting `text_color_light`.
  #   Any HTML color name or Hex value is valid.

  # Background color.
  # color = "navy"
  
  # Background gradient.
  # gradient_start = "DeepSkyBlue"
  # gradient_end = "SkyBlue"
  
  # Background image.
  # image = "headers/bubbles-wide.jpg"  # Name of image in `static/img/`.
  # image_darken = 0.6  # Darken the image? Range 0-1 where 0 is transparent and 1 is opaque.
  # image_size = "cover"  #  Options are `cover` (default), `contain`, or `actual` size.
  # image_position = "center"  # Options include `left`, `center` (default), or `right`.
  # image_parallax = true  # Use a fun parallax-like fixed background effect? true/false

  # Text color (true=light or false=dark).
  # text_color_light = true

[design.spacing]
  # Customize the section spacing. Order is top, right, bottom, left.
  padding = ["20px", "0", "20px", "0"]

[advanced]
 # Custom CSS. 
 css_style = ""
 
 # CSS class.
 css_class = ""
+++

<!-- # Date format for experience -->
<!-- #   Refer to https://sourcethemes.com/academic/docs/customization/#date-format -->
<!-- date_format = "Jan 2, 2006" -->

<!-- # Experiences. -->
<!-- #   Add/remove as many `[[experience]]` blocks below as you like. -->
<!-- #   Required fields are `title`, `company`, and `date_start`. -->
<!-- #   Leave `date_end` empty if it's your current employer. -->
<!-- #   Begin/end multi-line descriptions with 3 quotes `"""`. -->
<!-- [[experience]] -->
<!--   title = "Monday" -->
<!--   # company = "GenCoin" -->
<!--   # company_url = "" -->
<!--   # location = "California" -->
<!--   date_start = "2021-10-25" -->
<!--   date_end = "" -->
<!--   description = """ -->

```{r utils, echo = FALSE, message = FALSE}
library(tidyverse)
library(kableExtra)
my_palette <- spec_color(1:4, end = 0.9, option = "A", direction = -1)
get_color <- function(vec){
  sapply(vec, function(x) 
    if(x == "Master Class")
      return(my_palette[1])
    else if(x == "Invited talk")
      return(my_palette[2])
    else if(x == "Break")
      return(my_palette[4])
    else
      return(my_palette[3]))
}
```


## (It's got to be) Monday

```{r tableau_lundi, message = FALSE, eval = TRUE, echo = FALSE}
lundi <- data.frame(creneau = c("9h-10h30", "10h30-11h", 
                                "11h-11h30", "11h30-12h",  
                                "12h30-14h", "14h-15h", 
                                "15h-15h30", "15h30-16h",
                                "16h-16h30", "17h-17h30"),
                    talk_type = c("Master Class", "Break", 
                             "Contributed talk", "Contributed talk",
                             "Break", "Invited talk",
                             "Contributed talk", "Contributed talk",
                             "Break", "Invited talk"),
                    Speaker = c("TBA", "",
                                "TBA", "TBA",
                                "", "TBA",
                                "TBA", "TBA",
                                "", "TBA"),
                    Title = c("To be announced"),
                    Abstract = c("[Disponible ici](https://media1.tenor.com/images/618c6321f547133ca86ae55276c915d7/tenor.gif?itemid=15763066)"))
lundi %>%  
    mutate(talk_type = cell_spec(
      talk_type, color = "white", bold = T,
      background = get_color(talk_type)
    )) %>% 
  kableExtra::kbl(escape = FALSE,
             col.names = c("", "", "Speaker", "Title", "Abstract")) %>%
  kable_classic("striped")
```

## (Hooray for) Tuesday 

```{r mardi, echo = FALSE}
mardi <- lundi
mardi %>%  
    mutate(talk_type = cell_spec(
      talk_type, color = "white", bold = T,
      background = get_color(talk_type)
    )) %>% 
  kableExtra::kbl(escape = FALSE,
             col.names = c("", "", "Speaker", "Title", "Abstract")) %>%
  kable_classic("striped")
```

## (Waiting for) Wednesday

```{r mercredi, echo = FALSE}
mercredi <- lundi
mercredi %>%  
    mutate(talk_type = cell_spec(
      talk_type, color = "white", bold = T,
      background = get_color(talk_type)
    )) %>% 
  kableExtra::kbl(escape = FALSE,
             col.names = c("", "", "Speaker", "Title", "Abstract")) %>%
  kable_classic("striped")
```

## (Sweet) Thursday

```{r jeudi, echo = FALSE}
jeudi <- lundi
jeudi %>%  
    mutate(talk_type = cell_spec(
      talk_type, color = "white", bold = T,
      background = get_color(talk_type)
    )) %>% 
  kableExtra::kbl(escape = FALSE,
             col.names = c("", "", "Speaker", "Title", "Abstract")) %>%
  kable_classic("striped")
```

## (Aloha) Friday

```{r vendredi, echo = FALSE}
vendredi <- data.frame(creneau = c("9h-9h30", "9h30-10h", 
                                "10h-10h30", "10h30-11h",  
                                "11h-12h"),
                    talk_type = c("Contributed talk", "Contributed talk",
                                  "Contributed talk", "Break",
                                  "Prize session and closing"),
                    Speaker = c("TBA", "TBA", "TBA",
                                "", ""),
                    Title = c("To be announced"),
                    Abstract = c("[Disponible ici](https://media1.tenor.com/images/618c6321f547133ca86ae55276c915d7/tenor.gif?itemid=15763066)"))
vendredi %>%  
    mutate(talk_type = cell_spec(
      talk_type, color = "white", bold = T,
      background = get_color(talk_type)
    )) %>% 
  kableExtra::kbl(escape = FALSE,
             col.names = c("", "", "Speaker", "Title", "Abstract")) %>%
  kable_classic("striped")
```

